Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-23 summary.Rmd
intermediate commit to move stuff around

```{r, cache = TRUE}
zhat.bmp <- cluster.pabm(A.bmp, 2, use.all = TRUE, normalize = FALSE)
bmp.acc <- mean(zhat.bmp == z.bmp)

zhat.pb <- cluster.pabm(A.pb, 2, use.all = TRUE, normalize = FALSE, 
                        p = 2, q = 0, d.eigenmap = 2)
pb.acc <- mean(zhat.pb == z.pb)

zhat.dblp <- cluster.pabm(A.dblp, 2, use.all = TRUE, normalize = FALSE)
dblp.acc <- 1 - mean(zhat.dblp == z.dblp)
```

>>>>

```{r, cache = TRUE}
zhat.bmp <- cluster.pabm(A.bmp, 2, use.all = TRUE, normalize = FALSE)
bmp.acc <- mean(zhat.bmp == z.bmp)
bmp.acc <- ifelse(bmp.acc < .5, 1 - bmp.acc, bmp.acc)

zhat.pb <- cluster.pabm(A.pb, 2, use.all = TRUE, normalize = FALSE, 
                        p = 2, q = 0, d.eigenmap = 2)
pb.acc <- mean(zhat.pb == z.pb)
pb.acc <- ifelse(pb.acc < .5, 1 - pb.acc, pb.acc)

zhat.dblp <- cluster.pabm(A.dblp, 2, use.all = TRUE, normalize = FALSE)
dblp.acc <- mean(zhat.dblp == z.dblp)
dblp.acc <- ifelse(dblp.acc < .5, 1 - dblp.acc, dblp.acc)
```
